Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development

### 2016-12-16 ISORC2017/paper.tex
Update

% Package List
%\usepackage[dvips]{graphics}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

TINET (Tomakomai InterNETworking) \cite{url:TINET} is a compact TCP/IP protocol stack for embedded systems.
TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
TINET needs small memory for its TCP/IP protocol stack, therefore it is suitable for embedded systems.
However, there are several issues that TINET consists of many complex source codes.
It may take a lot of time for software developers to maintain, extend, and analysis the software because TINET is composed of many files and defines many macros.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET.

@@

    \item {\bf Improve configurability}

    \item {\bf Dynamic connection method}

    \item {\bf Support legacy codes}

    % \item {\bf Software visualization}

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS project.
To take restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.

@@

>>>>

% Package List
%\usepackage[dvips]{graphics}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small\ttfamily},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

TINET (Tomakomai InterNETworking) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
TINET needs small memory for its TCP/IP protocol stack, therefore it is suitable for embedded systems.
However, there are several issues that TINET consists of many complex source codes.
It may take a lot of time for software developers to maintain, extend, and analysis the software because TINET is composed of many files and defines many macros.

Component-based development is an approach to improve software productivity.
Component-based development is a design technique that can be applied to reusable software development \cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.
In addition, individual Component diagrams enable the visualization of an entire system.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, that component behaviors and interconnections are defined statically, thus TECS can optimize the overhead of componentization.

@@

    \item {\bf Improve configurability}\mbox{}\\
        TINET+TECS is a component-based system, therefore the software is flexible to change the configuration such as resize network buffer, add/remove TCP (or UDP) functions, and support both IPv4 and IPv6.
        In addition, a component diagram provides visualization of TINET, a complicated system.

    \item {\bf Dynamic connection method}\mbox{}\\

    \item {\bf Support legacy codes}\mbox{}\\
        TECS supports the adapter to call TECS functions from C codes, thus TINET+TECS can use an existing application.
    % \item {\bf Software visualization}

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
To take restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.
TINET has been released as open source.

@@

\subsection{send, receive specifier}

TECS supports send and receive specifiers, which are interface specifiers \cite{par:RPC}.
TINET+TECS uses send and receive specifiers instead of in and out to reduce the number of copies.

in is a specifier for input arguments.
A callee side uses the memory of arguments with in while executing the callee function.
When the processing returns to the caller side, the caller can reuse and deallocate the memory.

send is also a specifier for transferring data to a callee from a caller such as in.
The difference between in and send is whether to deallocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
In case of in specifier, both allocating and deallocating the data memory are performed in the caller.
On the other hand, in case of send, the caller allocates the data memory and the callee deallocates it.

out is a specifier for output arguments.
A callee writes data in the memory allocated by a caller, and the caller receives the data.

receive is also a specifier for a caller receiving data from a callee such as out.
The difference between out and receive is whether to allocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
While, in case of out, a callee writes data in the memory allocated by a caller, in case of receive, the callee allocates the data memory.
Deallocating the memory is performed in the caller in both cases.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start([send(sNetworkAlloc),size_is(size)]int8_t *outputp,
             [in]int32_t size,
             [in]uint8_t align);
  void read([receive(sNetworkAlloc),size_is(*size)]int8_t **inputp,
            [out]int32_t *size,
            [in]uint8_t align);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{An example of send and receive}
\label{src:SendReceive}
\end{figure}

### 2016-12-16 jssst/diff/1025.tex
Update

The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}, and utilizes two technologies: mruby and TECS.
In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mruby on TECS}) are described.

@@

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using a script language without slowing down the execution time.

\subsubsection{System Model of mruby on TECS}
The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/rotateReadyQueue.eps}
\caption{RiteVM scheduler design}
\label{fig:rotateReadyQueue}
\end{figure} 
\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/cyclic_handler.eps}
\caption{Component diagram of RiteVM scheduler}
\label{fig:cyclic_handler}
\end{figure}

@@

\subsection{Utilization of Component-Based Development}
% This section describes the design applying component-based development.
In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as components.
Therefore, developers can add, remove, or reuse these components easily.
For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import("tRiteVMScheduler.cdl");}.
CBD eliminates the need for developers to rewrite kernel configuration files.

@@

\section{Experimental Evaluation}
\label{sec:Evaluation}
This section discusses experimental results.
To analyze the advantages of the proposed framework, we evaluated the following.
\begin{itemize}
    \item Execution time of the platform
    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
    \item Execution time with singletasking, co-routine, and proposed multitasking
    \item Overhead for periodic time
    \item Synchronization of multiple RiteVM tasks
    \item Code size with CBD 
\end{itemize}

@@

\subsection{Improving Software Development Efficiency by Bluetooth Loader}

\begin{table}[t]
    \centering
\caption{Development procedure of existing and proposed frameworks}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c}
                            & Development procedure \\ \hline
        Exisiting framework &    (1) + (2) + (3)    \\ %\hline
        Proposed framework  &          (4)          \\ \hline
        \multicolumn{2}{l}{ (1): Rewrite the storage device} \\
        \multicolumn{2}{l}{ (2): Insert the storage device into the target} \\
        \multicolumn{2}{l}{ (3): Restart the RTOS on the target (about 4 sec)} \\
        \multicolumn{2}{l}{ (4): Transfer an mruby bytecode from host to target} \\
    \end{tabular}
    }
    \label{tab:procedure}
\end{table}

\begin{table}[t]
    \centering
\caption{Size and load process time of an mruby application with/without libraries}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c|c|c}
                        & App\&Lib     & App        &   App\&Lib/App  \\ \hline
        Bytecode Size   & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
        Loading Time    & 305.081 msec & 7.774 msec &   $\times$39.2          \\
        Compile Time    & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
    \end{tabular}
    }
    \label{tab:size_and_time}
\end{table}

The Bluetooth loader for mruby bytecode can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
In the proposed framework, the development procedure is shortened as shown Table \ref{tab:procedure}
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.
Note that the time of restarting the RTOS, including initializing device drivers, is 4 sec in case of the EV3 platform \cite{par:EV3}

@@

\subsection{RiteVM Scheduler}

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/comparison_s_c_m.eps}
\caption{Comparison of application execution time with singletask, co-routine, and multitask}
\label{fig:comparison_s_c_m}
\end{figure}

% A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig.\ref{fig:comparison_s_c_m}.
% A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
% Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.

%\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
{%\bf Execution Time with Singletasking, Co-routine, and Proposed Multitasking}

Fig.\ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
The {\it delay} and co-routine methods run on a RiteVM, which causes the slowdown compared to the proposed multitasking.
The scheduler runs as the periodic handler of RTOS.
% In Fig.\ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
% This shows that the proposed design is superior to co-routine in terms of execution time.

Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.Although the overhead is larger as the number of RiteVMs increases, it also spreads the difference between multitask and co-routine.
Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
It takes approximately 3 $\mu$sec on average to switch tasks once.

%\subsubsection{Periodic Time Overhead}
%{\bf Periodic Time Overhead}

Fig.\ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
The lower limit of the periodic time is 1 msec due to the specifications of TOPPERS/HRP2, i.e., the RTOS.
% More than 8 msec do not be evaluated in this paper because it is thought the larger periodic time influences applications.
The execution time decreases as the periodic time increases, because the number of switched tasks decreases.
Note that an execution time of 1 msec is approximately 1\% greater than that of 8 msec.
The RiteVM scheduler with a short periodic time can execute multiple tasks effectively because the periodic time overhead is not large.
Note that a smaller periodic time is better for multitasking due to concurrent or parallel processing.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/comparison_msec.eps}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
\label{fig:comparison_msec}
\end{figure}

\subsection{Synchronization of Multiple RiteVMs}

 \begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/eval_synchronization.eps}
\caption{Synchronization of multiple RiteVMs}
\label{fig:eval_synchronization}
\end{figure}

To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to that of the last RiteVM task.
It was confirmed that the time was within the theoretical value which is 
\begin{displaymath}
    {\scriptsize periodic\ time \times (number\ of\ RiteVM\ tasks - 1).}
\end{displaymath}
Fig.\ref{fig:eval_synchronization} shows the case of two to eight RiteVM tasks.
% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
Note that the periodic time is 1 msec.
As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.

\subsection{Benefits of Component-Based Development}

@@

In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
Developers can add or remove the functionalities easily by modifying the CDL file.
Moreover, CBD decreases code size and improves productivity and maintainability.

@@

\begin{table*}[t]
    \caption{Comparison of proposed and previous methods}
    \label{tab:comparison}
    \begin{center}
    {\tabcolsep=0.05cm
    \begin{tabular}{c||c|cccccc}
        & \shortstack{Bluetooth\\Loader}
        & \shortstack{Call\\C Function} 
        & \shortstack{Legacy Code of\\Embedded System} 
        & \shortstack{VM\\Management} 
        & \shortstack{VM\\Scheduler} 
        & \shortstack{Synchronization\\of Applications} \\ \hline
        ChaiScript \cite{url:ChaiScript}             &            &            &            &            &             &            \\
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark \\
    \end{tabular}
    }
    \end{center}
\end{table*}

Open-source runtime systems for scripting languages have been proposed such as ChaiScript\cite{url:ChaiScript}, python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

{\bf ChaiScript:} ChaiScript is a scripting language to be embedded in C++ applications.
It is a dialect of ECMAScript (a.k.a. JavaScript).
ChaiScript is header only, that is, it only needs to include the header files in order to be used it in an application.
ChaiScript will support co-routines, but not now.

@@

Table \ref{tab:comparison} compares the proposed framework to previous methods.
The proposed framework implements all of the features shown in the table.
In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
Note that the idea that a bytecode is transferred to the target device via Bluetooth can be applied to scripting languages other than mruby if the VM mechanism is used.

\section{Practical Use}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
In ET Robocon 2016, the team with the proposed framework stood second in a regional competition.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper presented an extended framework of mruby on TECS.
In the proposed framework, we implement a Bluetooth loader for mruby bytecode, a RiteVM scheduler, and synchronization mechanism.
The Bluetooth loader improves the software development efficiency because of omitting the process to rewrite a storage/ROM device and restart an RTOS on the target device.
The loader can use both Bluetooth and a wired serial connection, thus the proposed framework can be applied to various embedded systems.
The RiteVM scheduler makes multitasking more user-friendly compared to the current mruby on TECS.
Our experimental results show the advantages of the proposed framework.
The Bluetooth loader can improve the software development efficiency of mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.

The proposed framework is developed using CBD.
In addition, the RiteVMs, RiteVM scheduler, and Eventflags are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
Moreover, developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
For software developed with fixed-priority-based scheduling, developers only have to remove the RiteVM scheduler.
% Component-based development can increase productivity.
Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:download}.

>>>>

@@

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
% mruby on TECS is a component-based framework for running script language.
% This framework uses two technologies, mruby and TECS.

\subsubsection{System Model}
The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/rotateReadyQueue.eps}
\caption{RiteVM scheduler design}
\label{fig:rotateReadyQueue}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/cyclic_handler.eps}
\caption{Component diagram of RiteVM scheduler}
\label{fig:cyclic_handler}
\end{figure}

@@

@@

\subsection{Utilization of Component-Based Development}
% This section describes the design applying component-based development.
In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as components.
Therefore, developers can add, remove, or reuse these components easily.
For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import(<tRiteVMScheduler.cdl>);}.
CBD eliminates the need for developers to rewrite kernel configuration files.

@@

\begin{table}[t]
    \centering
\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c|c|c}
                        & App\&Lib     & App        &   App\&Lib/App  \\ \hline
        Bytecode Size   & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
        Loading Time    & 305.081 msec & 7.774 msec &   $\times$39.2          \\
        Compile Time    & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
    \end{tabular}
    }
    \label{tab:size_and_time}
\end{table}

\section{Experimental Evaluation}
\label{sec:Evaluation}
This section discusses experimental results.
To analyze the advantages of the proposed framework, we evaluated the following.
\begin{itemize}
%    \item Execution time of the platform
    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
    \item Execution time with singletasking, co-routine, and proposed multitasking
    \item Overhead for periodic time
    \item Synchronization of multiple RiteVM tasks
    \item Code size with CBD 
\end{itemize}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/comparison_s_c_m.eps}
\caption{Comparison of application execution time with singletask, co-routine, and multitask}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/comparison_msec.eps}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
\label{fig:comparison_msec}
\end{figure}

\subsection{Improving Software Development Efficiency by Bluetooth Loader}
The Bluetooth loader for mruby bytecode can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.

@@

\subsection{RiteVM Scheduler}
A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig.\ref{fig:comparison_s_c_m}.
A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.

\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
Fig.\ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
The {\it delay} and co-routine methods run on a RiteVM, which causes the slowdown compared to the proposed multitasking.
The scheduler runs as the periodic handler of RTOS.
% In Fig.\ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
% This shows that the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.Although the overhead is larger as the number of RiteVMs increases, it also spreads the difference between multitask and co-routine.
Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
It takes approximately 3 $\mu$sec on average to switch tasks once.

\subsubsection{Periodic Time Overhead}
Fig.\ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
The lower limit of the periodic time is 1 msec due to the specifications of TOPPERS/HRP2, i.e., the RTOS.
% More than 8 msec do not be evaluated in this paper because it is thought the larger periodic time influences applications.
The execution time decreases as the periodic time increases, because the number of switched tasks decreases.
Note that an execution time of 1 msec is approximately 1\% greater than that of 8 msec.
The RiteVM scheduler with a short periodic time can execute multiple tasks effectively because the periodic time overhead is not large.
Note that a smaller periodic time is better for multitasking due to concurrent or parallel processing.

 \begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/eval_synchronization.eps}
\caption{Synchronization of multiple RiteVM tasks}
\label{fig:eval_synchronization}
\end{figure}

@@

\subsection{Synchronization of Multiple RiteVM Tasks}
To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
Fig.\ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
As shown in Fig.\ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.

\subsection{Benefits of Component-Based Development}
In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
Developers can add or remove the functionalities easily by modifying the CDL file.
Moreover, CBD decreases code size and improves productivity and maintainability.

@@

\begin{table*}[t]
    \caption{Comparison of proposed and previous methods}
    \label{tab:comparison}
    \begin{center}
    {\tabcolsep=0.05cm
    \begin{tabular}{c||c|cccccc}
        & \shortstack{Bluetooth\\Loader}
        & \shortstack{Call\\C Function} 
        & \shortstack{Legacy Code of\\Embedded System} 
        & \shortstack{VM\\Management} 
        & \shortstack{VM\\Scheduler} 
        & \shortstack{Synchronization\\of Applications} \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
        ChaiScript \cite{url:ChaiScript}             &            &            &            &    -       &    -        &            \\
        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark \\
    \end{tabular}
    }
    \end{center}
\end{table*}

Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, ChaiScript\cite{url:ChaiScript}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

Table \ref{tab:comparison} compares the proposed framework to previous methods.
The proposed framework implements all of the features shown in the table.
In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
Note that the idea that a bytecode is transferred to the target device via Bluetooth can be applied scripting languages other than mruby if VM mechanism is used.

\section{Utilization Results}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
In ET Robocon 2016, the team with the proposed framework took second place at a regional competition.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper presents an extended framework of mruby on TECS, i.e., the proposed framework implements a Bluetooth loader for mruby bytecode and a RiteVM scheduler.
The Bluetooth loader improves software development efficiency by eliminating the need to rewrite a storage/ROM device and restart an RTOS.
The proposed framework can be applied to various embedded systems because the loader can use both Bluetooth and a wired serial connection.
%Thus, the proposed framework can be utilized on the devices without Bluetooth.
The RiteVM scheduler simplifies multitasking compared to the current mruby on TECS.
Our experimental results for the Bluetooth loader and RiteVM scheduler show their advantages.
The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.

The proposed framework is developed using CBD.
In addition, the RiteVMs, RiteVM scheduler, and Eventflags are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
Moreover, developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
For software developed with fixed-priority based scheduling, developers only have to remove the RiteVM scheduler.
% Component-based development can increase productivity.
Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:download}.

### 2016-12-16 jssst/diff/1027.tex
Update

@@

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
% mruby on TECS is a component-based framework for running script language.
% This framework uses two technologies, mruby and TECS.

\subsubsection{System Model}
The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

\subsection{Utilization of Component-Based Development}
% This section describes the design applying component-based development.
In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as components.
Therefore, developers can add, remove, or reuse these components easily.
For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import(<tRiteVMScheduler.cdl>);}.
CBD eliminates the need for developers to rewrite kernel configuration files.

@@

\section{Experimental Evaluation}
\label{sec:Evaluation}
This section discusses experimental results.
To analyze the advantages of the proposed framework, we evaluated the following.
\begin{itemize}
%    \item Execution time of the platform
    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
    \item Execution time with singletasking, co-routine, and proposed multitasking
    \item Overhead for periodic time
    \item Synchronization of multiple RiteVM tasks
    \item Code size with CBD 
\end{itemize}

@@

\section{Utilization Results}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
In ET Robocon 2016, the team with the proposed framework took second place at a regional competition.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper presents an extended framework of mruby on TECS, i.e., the proposed framework implements a Bluetooth loader for mruby bytecode and a RiteVM scheduler.
The Bluetooth loader improves software development efficiency by eliminating the need to rewrite a storage/ROM device and restart an RTOS.
The proposed framework can be applied to various embedded systems because the loader can use both Bluetooth and a wired serial connection.
%Thus, the proposed framework can be utilized on the devices without Bluetooth.
The RiteVM scheduler simplifies multitasking compared to the current mruby on TECS.
Our experimental results for the Bluetooth loader and RiteVM scheduler show their advantages.
The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.

>>>>

The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}, and utilize two technologies i.e., mruby and TECS.
In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mruby on TECS}) are described.

@@

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using script language without slowdown of the execution time.

\subsubsection{System Model of mruby on TECS}
The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

\subsection{Utilization of Component-Based Development}
% This section describes the design applying component-based development.
In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as components.
Therefore, developers can add, remove, or reuse these components easily.
For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import("tRiteVMScheduler.cdl");}.
CBD eliminates the need for developers to rewrite kernel configuration files.

@@

\section{Experimental Evaluation}
\label{sec:Evaluation}
This section discusses experimental results.
To analyze the advantages of the proposed framework, we evaluated the following.
\begin{itemize}
    \item Execution time of the platform
    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
    \item Execution time with singletasking, co-routine, and proposed multitasking
    \item Overhead for periodic time
    \item Synchronization of multiple RiteVM tasks
    \item Code size with CBD 
\end{itemize}

@@

\section{Actual Results}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
In ET Robocon 2016, the team with the proposed framework took second place at a regional competition.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper presented an extended framework of mruby on TECS.
In the proposed framework, we implements a Bluetooth loader for mruby bytecode, a RiteVM scheduler, and synchronization mechanism.
The Bluetooth loader improves software development efficiency because of omitting the process to rewrite a storage/ROM device and restart an RTOS on a target device.
The loader can use both Bluetooth and a wired serial connection, thus the proposed framework can be applied to various embedded systems.
The RiteVM scheduler makes multitasking more user-friendly compared to the current mruby on TECS.
Our experimental results show the advantages of the proposed framework.
The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
